Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 nge.tex

Pilots can offer a payload-independent scheduling interface while hiding the
mechanics of coordination and communication among multiple worker nodes. This
could eliminate the need for packaging payload into MPI scripts within the
broker, greatly simplifying the submission process. This simplification would
also enable the submission of different types of payload, without having to
develop a specific PBS script for each payload. The submission process would
also be MPI-independent, as MPI is used for coordination among multiple worker
nodes, not by the payload.

@@

NGE is a runtime system designed to execute heterogeneous and dynamic workloads
on diverse resources. Fig.~\ref{fig:arch-overview} illustrates its current
architecture as deployed on Titan: the two management modules represent a
simplified version of the PanDA Broker while the agent module is the pilot
submitted to Titan and executed on its worker nodes. The communication between
PanDA Broker and PanDA Server is abstracted away as not immediately useful to
evaluate the performance and capabilities of a pilot on Titan.

@@

The UnitManager and the Agent communicate via a database that is instantiated on
one of Titan's DTN so to be reachable by both modules. A similar approach would
be used to enable PanDA Broker to schedule pilots instead of MPI
scripts.\mtnote{Rewrite this after checking it with Andre.}

>>>>

Pilots can offer a payload-independent scheduling interface while hiding the
mechanics of coordination and communication among multiple worker nodes. This
could eliminate the need for packaging payload into MPI scripts within the
broker, greatly simplifying the submission process. This simplification would
also enable the submission of different types of payload, without having to
develop a specific PBS script for each payload. The submission process would
also be MPI-independent, as MPI is used for coordination among multiple worker
nodes, not by the payload. \jhanote{candidate for compression/contraction into
earlier paragraph(s)}

@@

NGE is a runtime system designed to execute heterogeneous and dynamic workloads
on diverse resources. Fig.~\ref{fig:arch-overview} illustrates its current
architecture as deployed on Titan: the two management modules represent a
simplified version of the PanDA Broker while the agent module is the pilot
submitted to Titan and executed on its worker nodes. The communication between
PanDA Broker and PanDA Server is abstracted away as it is not immediately useful to
evaluate the performance and capabilities of a pilot on Titan.

@@

The UnitManager and the Agent communicate via a database that is instantiated on
one of Titan's DTN so as to be reachable by both modules. A similar approach would
be used to enable PanDA Broker to schedule pilots instead of MPI
scripts.\mtnote{Rewrite this after checking it with Andre.}
